The Impact of Cloud Computing in $10$ Years

### 2013-05-06 essay/tex/essay.tex
revise done.

\section{Local Small Business and Cloud Computing}
How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in how it will impact the local small businesses.

%online-to-offline (O2O) business. The O2O business is the field that business connect online demands and offline convenience together, such as you can accurately discover a local product through online search or recommendation engines (sounds like an advanced e-business).

In fact, most local business either have their own website to present their products to consumers online or they have use the social media to advertise itself. However, they do not have a complete IT infrastructure stack for their business, especially the small business. Medium and big companies have their IT department or some vendors will provide the service for them. Therefore, those companies have their website, inventory management system, and business intelligence component. In addition, they can use eBay or Amazon to do better marketing work. In contrast, if we look at the local small businesses, such as a small local antique store, they usually do not have such a complete IT infrastructure. Cragilist is the most common used platform for them to advertise their product; and they may buy some basic inventory management system. As for the business intelligence, it is almost impossible for them to take advantage of this valuable tool.

The major reason for the small business to build a IT infrastructure is probably the cost. We cannot expect a local small store to spend thousands of dollars on the IT infrastructure, if they cannot make ten thousands of dollars profit per year. Fortunately, cloud computing could help them have a cheap and efficient IT infrastructure which could potentially improve their business over the years.

First, in my opinion, an intelligent marketplace is critical for the local business to broadcast their products. Some pioneer companies have entered into this field from different angels. Yelp is one of the local life information search engine which provides people with local restaurant, entertainment and special offers for the smartphone users. The cost for listing the products is free for Yelp and extra fees are charged for premium features. Zarrly is another company trying to build a bi-directional marketplace so that both buyers and sellers can post information and they provide a match engine to bring potential buyers and sellers together intelligently. These companies take advantages of cloud computing to establish their marketplace so that the local or small businesses can spend very little money to buy their services.

Second, an inventory management system and payment system are also very important to help the growth of a business. The typical cost of such a system is from several hundreds of dollars to thousands of dollars. Although the inventory management system may not be a big obstacle, the small or local business may expect an even cheaper solution. As for the payment system, not all local businesses support all the credit cards. For example, a very good Asian grocery store in Knoxville does not accept the American Express credit cards which make me very uncomfortable to buy something from their store. With the growing of mobile payment, companies like Google and Square has setup a convenient way to pay from smartphones or through the cloud. If the small stores in Knoxville can use their services, we do not need to worry about bringing cash or Visa cards before shopping in those stores.

Finally, the business intelligence system seems to be impossible for the small business right for two reasons: 1) the cost usually is usually not trivial; 2) the small businesss needs to use the inventory management and payment systems to keep track of their data in store but they usually do not have a complete service ready. However, if cloud computing can help the inventory management and payment systems, the business intelligence component is not a big deal, because it is just another machine learning or data mining component plug into the existing system in cloud.

However, the existing companies do not cover all those aspects. For example, eBay or Amazon could cover the intelligent marketplace, inventory management and payment system, but the business intelligence has not been under consideration yet. Google's Big Query is specifically for the analysis part but Google does not have a marketplace or inventory management system provided for the business. Even though I did not find any startups are working on the all-in-one in-cloud full stack infrastructure, but such a infrastructure from online marketplace, to inventory management, to the payment system and business intelligence could benefits the small business not only a cheap IT infrastructure but also make their whole business simpler and easier.

\section{Conclusion}
In this essay, I discussed some potential impacts that cloud computing cloud benefits for the academia and business in the next $10$ years. For the academia, what the primary and elementary education could benefit from cloud computing is the school IT infrastructure and teaching strategy. Paper-less course material and in-cloud course management system cloud replace the current ones in public school; and what the higher education could take advantages is the massive open online courseware which could bring more diversity to university students and make up unavailable courses in universities. On the other hand, for the business, I think the local small business could enjoy a lot from the cloud computing which could provide them an all-in-one in-cloud IT infrastructure at very low cost so that the local business could connect to both the online customers and offline ones very well.

>>>>

\section{Local Small Business and Cloud Computing}
How the business will use cloud computing in the future $10$ years is a board topic, but I am interested in how cloud computing will impact the local small businesses.

In fact, most local small business either have their own website to present their products to consumers online or they use the social media to advertise themselves. However, they do not have a complete IT infrastructure stack for their business. Medium and big companies have their IT department or some vendors will provide the service for them. Therefore, those companies have their website, inventory management system, and business intelligence component. In addition, they can use eBay or Amazon to do a better marketing work. In contrast, if we look at the local small businesses, such as a small local antique store, which usually does not have such a complete IT infrastructure. Cragislist is the most common used platform for them to advertise their product; and they may buy some basic inventory management system. As for the business intelligence, it is almost impossible for them to take advantage of this valuable tool.

The major reason prventing the small business to build a IT infrastructure is probably the cost. We cannot expect a local small store to spend thousands of dollars on the IT infrastructure, if they cannot make ten thousands of dollars profit per year. Fortunately, cloud computing could help them have a cheap and efficient IT infrastructure which could potentially improve their business over the years.

First, in my opinion, an intelligent marketplace is critical for the local business to broadcast their products. Some pioneer companies have entered into this field from different angels. Yelp~\cite{yelp} is one of the local life information search engine which provides local restaurant, entertainment and special offers for the smartphone users. The cost for listing the products is free for Yelp and extra fees are charged for premium features. Zarrly~\cite{zarrly} is another company trying to build a bi-directional marketplace so that both buyers and sellers can post information and they use a match engine to bring potential buyers and sellers together intelligently. These companies take advantages of cloud computing to establish their marketplace so that the local or small businesses can spend very little money to buy their services while obtaining high quality services.

Second, an inventory management system and payment system are also very important to help the growth of a business. The typical cost of such a system is from several hundreds of dollars to thousands of dollars. Although the inventory management system may not be a big obstacle, the local small business may expect an even cheaper solution. As for the payment system, not all local businesses support all types of credit cards. For example, a very good Asian grocery store in Knoxville does not accept the American Express credit cards which makes me very inconvenient to buy something from their store. With the growing of mobile payment, companies like Square~\cite{square} and Google have setup a convenient way to pay from smartphones or cloud. If the small stores in Knoxville can use their services, we do not need to worry about bringing cash or Visa cards before shopping in those stores.

Finally, the business intelligence system seems to be impossible for the small business for two reasons: 1) the cost usually is not trivial; 2) the small businesses need to use the inventory management and payment systems to keep track of their data in store but they usually do not have a complete service ready. Fortunately, if cloud computing can help the inventory management and payment systems, the business intelligence component is not a big deal, because it is just another machine learning or data mining component plug into the existing system in cloud.

However, the existing companies do not cover all those aspects. For example, eBay or Amazon could cover the intelligent marketplace, inventory management and payment system, but the business intelligence has not been under consideration yet. Google's Big Query~\cite{bigquery} is specifically for the analysis part but Google does not have a marketplace or inventory management system provided for the business. Even though I did not find any startups are working on the all-in-one in-cloud full stack infrastructure, but such an infrastructure from online marketplace, to inventory management, to the payment system and business intelligence could benefit the local small business not only a cheap IT infrastructure but also make their whole business simpler and easier.

\section{Conclusion}
In this essay, I discussed some potential impact that cloud computing can contribute to the academia and business in the next $10$ years. For the academia, what the primary and elementary education could be benefit from cloud computing is the school IT infrastructure and teaching strategy. Paper-less course material and in-cloud course management system cloud replace the current ones in public school; and what the higher education could take advantages is the massive open online courseware which could bring more diversity to university students and make up the unavailable courses in universities. On the other hand, for the business, I think the local small business could enjoy a lot from the cloud computing which could provide them an all-in-one in-cloud IT infrastructure at very low cost so that the local business could connect to both the online customers and offline ones very well.
